Review of "The elusive benefits of vagueness: the evidence so far"

### 2018-08-25 springer/review/vagueness-springer-review.tex
added some responses

\item Could you include a sample display for each experiment presented?
\marginnote[-.5cm]{8: \ldots}
\begin{quote}\ldots\end{quote}

@@

\item re: exp 2 presentation 3/3: what was the vague numeric instruction used in stimuli with larger dot arrays, e.g. (16,25,34)? [I assume it wasn't \emph{about 10}]
\marginnote[-0.5cm]{13: \ldots}
\begin{quote}\ldots\end{quote}

@@

\item p.17 \emph{we found a small (but statistically significant) disadvantage of vague instructions} -- again this is misleading since the effect is apparently driven almost entirely by a single condition (6, crisp) that was much faster than expected. There appear to be few differences otherwise \ldots one option would be to exclude the 6:15:24 condition and then re-run the statistical analysis to see if any other effects emerge.
\marginnote[-1.5cm]{17: \ldots}
\begin{quote}\ldots\end{quote}

@@

\item p.19 Testing (H1), we have \emph{Vague instructions were non-significantly easier \ldots} do you mean \emph{not significantly easier}? In any case from the graphs on the next page this seems misleading -- what it looks like is a substantial main effect where vague instructions have a main effect of lowering the response time, but this effect is masked by interactions with quantity, most notably (again) the huge speed-up for 6 in the matching/crisp condition. I'd recommend following the method described in Roger Levy's paper on finding main effects in the presence of interactions (\url{https://arxiv.org/abs/1405.2094}).
\marginnote[-1.5cm]{19: \ldots}
\begin{quote}\ldots\end{quote}

\item p.20 \emph{the cost reduction account was wrong to predict significant main effect advantages for vagueness} -- this seems way too strong given the issues I've just described. First, the statistical analysis needs to be redone as I just mentioned. Second, in the kind of statistical analysis being employed here it's not possible to show that something doesn't exist simply by failing to find evidence that it does exist. (APA guidelines: \emph{Never use the unfortunate expression "accept the null hypothesis"}, cf. Wagenmakers (\url{http://www.ejwagenmakers.com/2007/pValueProblems.pdf}). At best, you can say \emph{we failed to find evidence that \ldots}
\marginnote[-1.5cm]{20: \ldots}
\begin{quote}\ldots\end{quote}

@@

\item p.22 \emph{In the matching task vagueness slowed response times} -- again this is not a good summary since there is a big interaction, and the apparent main efect may be driven by a single condition, here a slowdown for 6:15:24 in the matching/vague condition. Re-running using Levy's method would be advisable here.
\marginnote[-1.5cm]{23: \ldots}
\begin{quote}\ldots\end{quote}

>>>>

\item Could you include a sample display for each experiment presented?
\marginnote[-.5cm]{8: done}
\begin{quote}We added sample displays for each experiment presented.\end{quote}

@@

\item re: exp 2 presentation 3/3: what was the vague numeric instruction used in stimuli with larger dot arrays, e.g. (16,25,34)? [I assume it wasn't \emph{about 10}]
\marginnote[-0.5cm]{13: done\ldots}
\begin{quote}We have provided full tables of instructions.\end{quote}

@@

\item p.17 \emph{we found a small (but statistically significant) disadvantage of vague instructions} -- again this is misleading since the effect is apparently driven almost entirely by a single condition (6, crisp) that was much faster than expected. There appear to be few differences otherwise \ldots one option would be to exclude the 6:15:24 condition and then re-run the statistical analysis to see if any other effects emerge.
\marginnote[-1.5cm]{17: done in the online supplement but not yet added to the document}
\begin{quote}done in the online supplement but not yet added to the document\end{quote}

@@

\item p.19 Testing (H1), we have \emph{Vague instructions were non-significantly easier \ldots} do you mean \emph{not significantly easier}? In any case from the graphs on the next page this seems misleading -- what it looks like is a substantial main effect where vague instructions have a main effect of lowering the response time, but this effect is masked by interactions with quantity, most notably (again) the huge speed-up for 6 in the matching/crisp condition. I'd recommend following the method described in Roger Levy's paper on finding main effects in the presence of interactions (\url{https://arxiv.org/abs/1405.2094}).
\marginnote[-1.5cm]{19: done}
\begin{quote}This is done for D exp 2. The effect was not significant when using levy's method\end{quote}

\item p.20 \emph{the cost reduction account was wrong to predict significant main effect advantages for vagueness} -- this seems way too strong given the issues I've just described. First, the statistical analysis needs to be redone as I just mentioned. Second, in the kind of statistical analysis being employed here it's not possible to show that something doesn't exist simply by failing to find evidence that it does exist. (APA guidelines: \emph{Never use the unfortunate expression "accept the null hypothesis"}, cf. Wagenmakers (\url{http://www.ejwagenmakers.com/2007/pValueProblems.pdf}). At best, you can say \emph{we failed to find evidence that \ldots}
\marginnote[-1.5cm]{20: \ldots}
\begin{quote}I have toned the language down here (after also re-doing the statitical analysis in the requested way\end{quote}

@@

\item p.22 \emph{In the matching task vagueness slowed response times} -- again this is not a good summary since there is a big interaction, and the apparent main efect may be driven by a single condition, here a slowdown for 6:15:24 in the matching/vague condition. Re-running using Levy's method would be advisable here.
\marginnote[-1.5cm]{23: done\ldots}
\begin{quote}This is done for E exp 3. The effect was not significant when using levy's method\end{quote}
